\thetitle

### 2017-12-22 TeX/manuscript.tex
made diagram for section 2.4

>>>>

\subsection{Combining computation through conditional statements}
% https://en.wikipedia.org/wiki/Abstract_syntax_tree#/media/File:Abstract_syntax_tree_for_Euclidean_algorithm.svg

	Conditional statements, such as $if$ and $while$ may be used to combine categorical and numerical computation. Each conditional statement accepts an input expression, and has a body which is defined before runtime. If the input expression evaluates to $True$, then the statement will execute whatever is in the body. The body may contain computations of any kind, including numerical. In the following examples, conditional statements are used to execute some numerical computations depending on the result of some categorical computations.

\begin{figure}

	\tikzstyle{operation} = [shape=rectangle, draw, outer sep=0,inner  sep=6,minimum size=15, fill = blue!32]
	\tikzstyle{value} = [shape=rectangle, draw, outer sep=0,inner  sep=6,minimum size=15, fill = green!40]
 	\tikzstyle{function} = [shape=rectangle, draw, outer sep=0,inner  sep=6,minimum size=15, fill = red!40]
	\tikzstyle{con} = [thick,->]

	\node[function] (StatementSequence) at (9,7) {Statement Sequence};

	\node[operation] (return) at (13,5.5) {return};
	\node[value] (returnVal) at (13,3.5) {NumPrimes};

	\draw[->](StatementSequence) -> (return) ;	
	\draw[->](return) -> (returnVal) ;

	\node[operation] (while) at (6,4) {while};
	\node[value] (CurrentValue) at (0,0) {CurrentValue};
	\node[value] (MaxValue) at (3,0) {MaxValue};
	\node[operation] (lessThan) at (1.5,2.5) {compare op: $<=$};

	\draw[->](StatementSequence) -> (while) ;	
	\draw[->](while) -> (lessThan) node[midway,sloped,above] {condition} ;	
	\draw[->](lessThan) -> (MaxValue) ;	
	\draw[->](lessThan) -> (CurrentValue) ;

	\node[operation] (incrementCurr) at (6,2.5) {CurrentValue++};
	\draw[->](while) -> (incrementCurr) ;

	\node[operation] (branch) at (10.5,2.5) {branch};
	\node[function] (isPrime) at (9,0) {isPrime(CurrentValue)};
	\node[operation] (incrementPrime) at (13,0) {NumPrimes++};

	\draw[->](while) -> (branch) ;
	\draw[->](branch) -> (isPrime)  node[midway,sloped,above] {condition};		
	\draw[->](branch) -> (incrementPrime)  node[midway,sloped,above] {if-body};

\caption{A syntax tree that defines a procedure for counting the number of primes up to a certain value. The procedure begins with NumPrimes and CurrentValue set to $0$, and MaxValue set to the highest value to check for prime status. isPrime is a function that returns $True$ if the input value is a prime number, and $False$ if it isn't.}

\end{figure}
